---
title: "Channel cross section"
author: "Tim Covino"
date: "4/19/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, results = FALSE)
```

```{r}
#Packages needed for this project

library(tidyverse)
library(here)

```

## Read in the data frame.
```{r}
df <- read_csv(here('hydrology/src_classes_spring_2022/data/channel_df.csv'))
```

## Let's plot the raw data
```{r}
df %>% 
  ggplot(aes(x = Width_m, y = Channel_height_m, color = Location)) +
  geom_point() +
  geom_line()
```

## Now lets invert the channel height.
```{r}
df %>% 
  mutate(invert_height = 1 - Channel_height_m) %>% 
  ggplot(aes(x = Width_m, y = invert_height, color = Location)) +
  geom_point() +
  geom_line()
  
```

## That is starting to look OK. Now let's add the water level.
```{r, fig.cap = "Figure 1. Cross-sectional data for the Poudre River at the Environmental Learning Center April 2022."}

df <- df %>% 
  mutate(invert_height = 1 - Channel_height_m, new_water = Water_level_m + invert_height) 

df %>% 
  ggplot() +
  geom_point(aes(x = Width_m, y = invert_height, color = Location), alpha = 0.5, size = 3) +
  geom_line(aes(x = Width_m, y = invert_height, color = Location)) +
  geom_line(aes(x = Width_m, y = new_water), color = "blue", size = 1.5) +
  geom_point(aes(x = Width_m, y = new_water), color = "blue", alpha = 0.5, size = 3)+ 
  ylab("Height (m)") +
  xlab("Width (m)") +
  theme_linedraw() +
  theme(legend.title = element_blank())


```

## And to calculate the area of the channel. The first part is the linear interpolation.You will note that cor_d does have one negative value. You could remove that with a filter. 
```{r}
seq <- seq(from = 0.02, to = 0.17, length.out = 61)

df <- cbind(df, seq) %>% 
  mutate(cor_d = Channel_height_m - seq)

df <- df %>% 
  mutate(area_m2 = (lead(Width_m) - lag(Width_m)) / 2 *cor_d)

total_area <- sum(df$area_m2, na.rm = TRUE)
```


## We could also calculate the wetted area, mean BF-depth, etc. I don't have the notes on location of BF, so I'll just do wetted area. 

```{r}
df <- df %>% 
  mutate(wetted_area_m2 = (lead(Width_m) - lag(Width_m)) / 2 *
  Water_level_m)

total_wetted_area <- sum(df$wetted_area_m2, na.rm = TRUE)
```










