---
title: "Dilution gauging"
author: "Tim Covino"
date: "9/30/2021"
output: html_document
---
```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, results = FALSE)
```


## The libraries we will need. Remember to install the packages if you need. 
```{r}
library(tidyverse)
library(here)
library(plotly)
library(lubridate)
library(tibbletime)
```

## Load data and make the time a tbl time to allow for indexing. We will use that later to return times to 5%, 50%, and 95% recovery of tracer. 
```{r}
df_assess <- read_csv(here('hydrology/3_dilution_gauging/R/data/corrected_conductivity_working.csv'))

df <- read_csv(here('hydrology/3_dilution_gauging/R/data/COND_data_4_26_22.csv'))

df_assess_tt <- as_tbl_time(df_assess, index = Time)
df_tt <- as_tbl_time(df, index = Time) 

```

## Do a plotly to look at data
```{r}
ggplotly(df_assess_tt %>%
  ggplot(aes(x = Time, y = Cond_cor)) +
  geom_point()
    )
```
 
## Let's add in metadata
```{r}
dist <- 20 

## injection 1
mass1<-223.8
injTime1 <- "15:11:35"
endTime1 <- "15:24:00"
## injection 2
mass2<-418.4
injTime2 <- "15:21:40"
## injection 3
mass3<-312.6
injTime3 <- "15:41:45"
```

## Here we will filter the data frame down to the data for each injection. 
```{r}
inj_1 <- df_assess_tt %>% 
  filter_time(injTime1 ~ endTime1) %>% 
  mutate(time_since_inj = Run_time - 2045)

```

## We need to correct the tracer data for background concentrations. So let's look at the data and determine background. 
```{r}
ggplotly(inj_1 %>% 
  ggplot() +
  geom_point(aes(x = time_since_inj, y = Cond_cor))
)

inj_1 <- inj_1 %>% 
  mutate(bg_sc = Cond_cor - 0.75) %>% 
  filter(bg_sc > 0)

```

## And then we should plot that to make sure it looks good. 
```{r}
ggplotly(inj_1 %>% 
  ggplot(aes(x = time_since_inj, y = bg_sc)) +
  geom_point() +
    labs(x = 'Time since injection (s)', y = 'SC (uS/cm)')
  )
```

## Next we need to do the integration.
```{r}
inj_1 <- inj_1 %>% 
  mutate(NaCl = bg_sc/2) %>% # convert from conductivity (mS/cm) to concentration NaCl (g/L)
  mutate(IntC_s1 = NaCl+lag(NaCl, default=0)) %>% # begin integration through addition 
  mutate(IntC = cumsum(IntC_s1*.5*5)) %>% # complete integration
  mutate(recovery = IntC/max(IntC)) # Convert to relative recovery vayring from 0 to 1

```

```{r}
ggplotly(inj_1 %>% 
  ggplot() +
  geom_point(aes(x = time_since_inj, recovery)) +
  theme_linedraw() +
  labs(x = 'Time since injection (s)', y = 'Relative tracer recovery (-)') 
)
```

## We can use those data to make some velocity calculations. Recall that we will calculate the arrival, peak, median, and exit travel times. 
```{r}
# We can use the ggplotly to determine time to peak, which is the modal velocity. 

ttp <- 210

fiveRecovery.idx1<- which.min(abs(inj_1$recovery-.05)) # find the index of the point that has recovery equal to .05 (or 5%)
fiftyRecovery.idx1<- which.min(abs(inj_1$recovery-0.5))
ninetyfiveRecoery.idx1<- which.min(abs(inj_1$recovery-0.95))

five_time <- inj_1[26, 4]
#fifty_time <- inj_1[]
#ninety_five_time <- inj_1[]


five_vel <- dist/five_time
#fifty_vel <- dist/fifty_time
#ninety_five_vel <- dist/ninety_five_time

```


```{r}
# Determine flow
Q1 <- mass1/max(inj_1$IntC)

```


## Now you can repeat these steps for slugs 2 and 3. 

inj_2 <- df_tt %>% 
  filter_time(injTime2 ~ endTime2) #%>% 
  mutate(time_since_inj = Run_time - 2650)

inj_3 <- df_tt %>% 
  filter_time(injTime3 ~ endTime3) #%>% 
  mutate(time_since_inj = Run_time - 3855)






