---
title: "WR417 Final Project: Delineating Watersheds"
author: "Marin MacDonald and Alex Merklein"
date: '2022-05-11'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sf)
library(mapview)
library(nhdplusTools)

mapviewOptions(fgb = FALSE)
```

# Overview
This project will focus on how to delineate watersheds using two different methods. The first, using ArcGIS Pro and StreamStats, and the other, using ndhdPlus Tools in R. 

# Packages 
The packages required for this lesson include: \n

  -Tidyverse, in order to use pipes\n

  -mapview, in order to map the delineated watersheds\n

  -nhdplusTools, to delineate the watershed\n

# Using StreamStats to Delineate Watersheds
For this method of delineating watersheds, we will be using [StreamStats](https://streamstats.usgs.gov/ss/), a program run by the USGS which allows flowlines to be selected, and returns stats on the chosen watershed. 
The site that we are going to be using for our watershed delineation is in Greeley, Colorado.

**Station ID:** 06752500

**Station Name:** CACHE LA POUDRE RIVER NEAR GREELEY, CO.

**Latitude:** 40.41776

**Longitude:** -104.64

## Methods in StreamStats
1. Go to “search for a place”, enter the station ID, and select Colorado as the State. This will
bring you to the part where you delineate your watershed.

2. Click the Delineate button and then click on one of the blue pixels near our site. This process
may take a few minutes.
(Reference Q2_Image)

3. Before we collect the data for Arc select DRNAREA under basin characteristics, continue, and
open report. How large is the drainage area for this watershed?

4. Once this process is completed you will see a view of the watershed that we are delineating.
  - You will now click the “Download Basin” button and select the ShapeFile option.
  - This will give you a zip file containing the data we need for ArcGIS Pro
  - Extract the layers folder and its contents to a folder of your choice (to make things easier
you should create a folder in which you will keep your data and ArcGIS project in. This
will make navigating to the files you’ll need easier)
(Reference Q4_Image)

## Methods In ArcGIS Pro
5. Create a new ArcGIS project and import the data from StreamStats by right clicking Map
under drawing order and select add data. Navigate to your layers file location and select the two.shp files. 
Now we have our data in Arc!

6. We now want to change the projection of our map so we can take more accurate
measurements of this watershed. To do this you will want to right-click on map go to **Properties – Coordinate Systems – Projected Coordinate System – State Plane – NAD 1983 (2011) (Meters) – StatePlane Colorado North FIPS 0501**
(Reference Q6_Image)

7. Now that we have changed the coordinate system, we can now calculate the area for this
watershed. To do this you will select Measure under the map tab, select Measure Features, and
click on the watershed boundary polygon (make sure that you select Metric for the units to be
displayed in). What is the area that you found? How does the area differ from the drainage areacollected from Stream Stats?

# Using ndhPlus Tools in R
#Downloading the data
Using the ndhPlus Tools, download the HUC8 for the Cache la Poudre Watershed. 
```{r}
# Download the huc 8 for the Poudre River using its USGS code
poud <- get_huc8(id = "10190007" )
# This will give you an outline of the Poudre River watershed, with metadata

```

Now that the data has been downloaded, we can add the flowlinesof the watershed, similar to the flowlines in StreamStats.
```{r}
# Next, we can get the flowlines (all the streams) in the watershed 
poud_flowlines <- get_nhdplus(AOI = poud, 
                         realization='flowline') # selects flowline in the search
```

Finally, plot your delineated watershed. 
```{r}
#Plot your watershed using mapview!
mapview(poud_flowlines, color = "darkblue") + mapview(poud, color = "lightblue")

```
Now, we have an interactive map of the Cache la Poudre watershed, with all of the streams within it! 

If we want to make a more in-depth map of our watershed, we can include catchments and water bodies in our map too. 

```{r}
poud_catchments <- get_nhdplus(AOI=poud, 
                          realization='catchment') 
poud_waterbodies <- get_waterbodies(AOI=poud)
mapview(poud_catchments, color = "purple") + mapview(poud_waterbodies, color = "darkblue")+
mapview(poud, color = "lightblue") 
```
This map includes the catchments within the watershed, as well as the bodies of water located within it. 

# Discussion
How do these methods differ? 
Is there one that you think is easier?
When is each method more useful?

# Practice 
Select different watersheds in Colorado by searching their HUC 8 codes online. Using the nhdPlus Tools method in R, complete the steps above and map each watershed. 
Explore the nhdPlus Tools, are there any others that would be useful for delineating watersheds? 
(Hint: watershed area and elevation are tools in the nhdplus package!)
