---
title: "csasn_tascc_no3_po4"
author: "tim covino"
date: "9/25/2020"
output: html_document
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(viridis) 
library(kableExtra)
library(knitr)
library(lubridate)
library(hms)
library(here)
library(ggplot2)
library(plotly)
library(ggthemes)
library(broom)
library(dplyr)
install.packages("psych")          
library("psych")  

```


##Load data
```{r}
df <- read_csv(here('data', 'p_in_8_2_11_A_up.csv'))
info <- read_csv(here('data', 'p_in_8_2_11_info.csv'))
Chart_title = paste('P-In A Up', '8/2/11', sep=" ")

```


## Let's declare some variables
```{r}
Q <- info$Q
w <- info$w
loc = 'up'

#For I8-In: up = 340, down = 555; I8-Out: up = 260, down = 360; P-In: up = 90, down = 140 m in 2010 and 120 in 2011
dist <- ifelse(loc == 'up', 90, 120)

NaCl <- info$NaCl_a
NaNO3 <- info$NaNO3
KH2PO4 <- info$KH2PO4

cl_inj <- NaCl*(0.6066) 
no3_n_inj <- NaNO3*(0.1648)
po4_p_inj <- KH2PO4*(0.2276)

no3_cl_inj <- (no3_n_inj/cl_inj)
log_no3_cl_inj <- log(no3_cl_inj)
p_cl_inj <- (po4_p_inj/cl_inj)
log_p_cl_inj <- log(p_cl_inj)

```


##Truncate data set to clip tails if needed
```{r}
ggplotly(ggplot(df,aes(x = Time, y = Cl)) +
  geom_point() + 
  ggtitle(Chart_title) +  
  theme_few())


df <- df %>%  
  mutate(Time = as_hms(Time)) %>% 
      filter(Time >= hms::as_hms('14:14:00'),
             Time <= hms::as_hms('15:50:00'))

```


##Background corrections
```{r}
#Now background correct the BTC data
bg_no3 <- min(df$NO3_N, na.rm = TRUE) 
df <- mutate(df, cor_no3 = NO3_N - bg_no3*0.9975)

bg_p <- min(df$PO4_P, na.rm = TRUE)
df <- mutate(df, cor_p = PO4_P - bg_p*0.9975)

df <- mutate(df, cl_ug = Cl*1000)
bg_cl <- min(df$cl_ug, na.rm = TRUE)
df <- mutate(df, cor_cl = cl_ug - bg_cl*0.9975) 

```


##Calculate total concentration
```{r}
#For nitrate
df <- mutate(df, con_no3 = no3_cl_inj * cor_cl) %>%
  mutate(con_amb_no3 = con_no3 + bg_no3) %>%
  rowwise() %>% 
  mutate(tot_no3 = geometric.mean(c(con_amb_no3, NO3_N), na.rm=T)) 


#For phosphate
df <- mutate(df, con_p = p_cl_inj * cor_cl) %>%
  mutate(con_amb_p = con_p + bg_p)%>%
  rowwise() %>% 
  mutate(tot_p = geometric.mean(c(con_amb_p, PO4_P), na.rm=T)) 

```


##Make TASCC calcs
```{r}

#For nitrate             
df <- mutate(df, no3_cl = cor_no3/cor_cl) %>%
  mutate(no3_cl = replace (no3_cl, which(no3_cl>no3_cl_inj), NA)) %>%
  mutate(log_no3_cl = log(no3_cl)) %>%
  mutate(diff_no3 = log_no3_cl - log_no3_cl_inj) %>%
  mutate(kw_no3 = diff_no3/dist) %>%
  mutate(sw_no3 = -1/kw_no3)

#For phosphate
df <- mutate(df, p_cl = cor_p/cor_cl) %>%
  mutate(p_cl = replace (p_cl, which(p_cl>p_cl_inj), NA)) %>%
  mutate(log_p_cl = log(p_cl))%>%
  mutate(diff_p = log_p_cl - log_p_cl_inj) %>%
  mutate(kw_p = diff_p/dist) %>%
  mutate(sw_p = -1/kw_p)

```


##Plot Sw vs. concentration and inspect relationship
```{r}
#For nitrate
ggplotly(ggplot(df, aes(x = Time, y = sw_no3)) +
  geom_point(size = 3) +
  geom_line() +
  theme_few())

ggplotly(ggplot(df, aes(x =tot_no3, y = sw_no3)) +
  geom_point() +
  theme_few() +
  stat_smooth(aes(group = 1), method='lm', color = 'black') +
  ggtitle(Chart_title) +
  expand_limits(x = 0, y = 0))

#For phosphate
ggplotly(ggplot(df, aes(x = Time, y = sw_p)) +
  geom_point(size = 3) +
  geom_line() +
  theme_few())

ggplotly(ggplot(df, aes(x =tot_p, y = sw_p)) +
  geom_point() +
  theme_few() +
  stat_smooth(aes(group = 1), method='lm', color = 'black') +
  ggtitle(Chart_title) +
  expand_limits(x = 0, y = 0))

```


##Remove outliers through visual inspection. It is often necessary to remove values on the tails. 
```{r}

##If they exist, remove high outliers in nitrate data set
df <- mutate(df, sw_no3 = replace (sw_no3, which(sw_no3>200), NA))  

##If they exist, remove high outliers in phosphate data set
df <- mutate(df, sw_p = replace (sw_p, which(sw_p>75000), NA))  

```


##Fit linear model and retrieve paramater values for nitrate
```{r}

#For nitrate
sw_no3.lm = lm(sw_no3 ~ tot_no3, data=df) 
summary(sw_no3.lm)

#get Sw-amb value from summary of sw_no3.lm
Sw_amb_no3 = coef(sw_no3.lm)['(Intercept)']  # units are m


#Convert Sw-amb to U-amb
U_amb_no3 = ((Q * bg_no3)/(Sw_amb_no3 *w)) * 60  # units are ug/m2/min

#Convert U-amb to Vf-amb
Vf_amb_no3 = U_amb_no3/bg_no3  # units are mm/mi

sum_no3 <- c('Vf_amb_no3' = Vf_amb_no3, Chart_title) 
print(sum_no3)   

```


##Fit linear model and retrieve paramater values for phosphate
```{r}

#For phosphate
sw_p.lm = lm(sw_p ~ tot_p, data=df)
summary(sw_p.lm)


#get Sw-amb value from summary of sw_p.lm
Sw_amb_p = coef(sw_p.lm)['(Intercept)']  # units are m

#Convert Sw-amb to U-amb
U_amb_p = ((Q * bg_p)/(Sw_amb_p *w)) * 60  # units are ug/m2/min

#Convert U-amb to Vf-amb
Vf_amb_p = U_amb_p/bg_p  # units are mm/mi

sum_p <- c('Vf_amb_p' = Vf_amb_p, Chart_title) 

print(sum_p)   

write_csv(df,here('data/publication_data','p_in_a_up_8_2_11.csv'))
```


