---
title: "csasn regressions"
author: "tim covino"
date: "11/16/2020"
output: html_document
---


```{r setup, echo=F, message=F }
library(tidyverse)
library(lubridate)
library(here)
library(scales)
library(readxl)

```


```{r}
data <- read_csv(here('data', 'csasn_vf_metab_env_p_values_long_11_13_20.csv'))

na <- read_csv(here('data', 'csasn_vf_metab_env_p_values_NA.csv')) #this includes the 0 uptake measurements
  

par <- read_xlsx(here('data/PAR_2011.xlsx'))

c <- read_xlsx(here('data/Q_C_rain_data.xlsx'))


```


Do regressions for I8-In alone
```{r}
i8in <- data %>%
  filter(Site == 'I8-In')

i8in_wide <- i8in %>% 
  pivot_wider(names_from = nutrient, values_from = Conc)

write.table(i8in_wide, file = 'ms/i8_in_wide.txt', sep = ',', quote = FALSE, row.names = F)

i8in_nh4 <- i8in %>% 
  filter(nutrient == 'NH4-N')

i8in_no3 <- i8in %>% 
  filter(nutrient == 'NO3-N')

i8in_po4 <- i8in %>% 
  filter(nutrient == 'PO4-P')
```


Here are the regressions of physical parameters vs Vf for I8-In
```{r}

#Get summary stats for lm on NH4_Vf at I8-In
i8in_temp_NH4_Vf.lm = lm(Vf ~ Temp, data = i8in_nh4)
summary(i8in_temp_NH4_Vf.lm)
rm(i8in_temp_NH4_Vf.lm)

i8in_PAR_NH4_Vf.lm = lm(Vf ~ PAR, data = i8in_nh4)
summary(i8in_PAR_NH4_Vf.lm)
rm(i8in_PAR_NH4_Vf.lm)

i8in_Q_NH4_Vf.lm = lm(Vf ~ Q, data = i8in_nh4)
summary(i8in_Q_NH4_Vf.lm)
rm(i8in_Q_NH4_Vf.lm)

i8in_N_NH4_Vf.lm = lm(Vf ~ Conc, data = i8in_nh4)
summary(i8in_N_NH4_Vf.lm)
rm(i8in_N_NH4_Vf.lm)

#Get summary stats for lm on NO3_Vf at I8-In
i8in_temp_NO3_Vf.lm = lm(NO3_Vf ~ Temp, data = i8in_no3)
summary(i8in_temp_NO3_Vf.lm)
rm(i8in_temp_NO3_Vf.lm)

i8in_PAR_NO3_Vf.lm = lm(NO3_Vf ~ PAR, data = i8in_no3)
summary(i8in_PAR_NO3_Vf.lm)
rm(i8in_PAR_NO3_Vf.lm)

i8in_Q_NO3_Vf.lm = lm(NO3_Vf ~ Q, data = i8in_no3)
summary(i8in_Q_NO3_Vf.lm)
rm(i8in_Q_NO3_Vf.lm)

i8in_N_NO3_Vf.lm = lm(NO3_Vf ~ NO3, data = i8in_no3)
summary(i8in_N_NO3_Vf.lm)
rm(i8in_N_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at I8-In
i8in_temp_PVf.lm = lm(Vf ~ Temp, data = i8in_po4)
summary(i8in_temp_PVf.lm)
rm(i8in_temp_PVf.lm)


i8in_PAR_PVf.lm = lm(Vf ~ PAR, data = i8in_po4)
summary(i8in_PAR_PVf.lm)
rm(i8in_PAR_PVf.lm)

i8in_Q_PVf.lm = lm(Vf ~ Q, data = i8in_po4)
summary(i8in_Q_PVf.lm)
rm(i8in_Q_PVf.lm)

i8in_P_PVf.lm = lm(Vf ~ Conc, data = i8in_po4)
summary(i8in_P_PVf.lm)
rm(i8in_P_PVf.lm)


```


Generic plotting for visual assessment of data
```{r}

ggplotly(ggplot(i8out_po4,aes(x = GPP, y = Vf, color = Site)) + geom_point() + 
  #ylab(expression(NH[4]-N~V[f-amb]~(mm/min))) + 
  theme_bw(base_size = 16)) #+
  #xlab(expression ("GPP (g/m"^2*"/d)")) +
  #geom_smooth(method='lm', color = "black"))

```


Do regressions for I8-Out alone
```{r}
i8out <- data %>%
  filter(Site == 'I8-Out')

i8out_nh4 <- i8out %>% 
  filter(nutrient == 'NH4-N')

i8out_no3 <- i8out %>% 
  filter(nutrient == 'NO3-N')

i8out_po4 <- i8out %>% 
  filter(nutrient == 'PO4-P')

```


Here are the regressions of physical parameters vs Vf for I8-Out
```{r}

#Get summary stats for lm on NH4_Vf at I8-Out
i8out_temp_NH4_Vf.lm = lm(Vf ~ Temp, data = i8out_nh4)
summary(i8out_temp_NH4_Vf.lm)
rm(i8out_temp_NH4_Vf.lm)

i8out_PAR_NH4_Vf.lm = lm(Vf ~ PAR, data = i8out_nh4)
summary(i8out_PAR_NH4_Vf.lm)
rm(i8out_PAR_NH4_Vf.lm)

i8out_Q_NH4_Vf.lm = lm(Vf ~ Q, data = i8out_nh4)
summary(i8out_Q_NH4_Vf.lm)
rm(i8out_Q_NH4_Vf.lm)

i8out_N_NH4_Vf.lm = lm(Vf ~ Conc, data = i8out_nh4)
summary(i8out_N_NH4_Vf.lm)
rm(i8out_N_NH4_Vf.lm)

#Get summary stats for lm on NO3_Vf at I8-Out
i8out_temp_NO3_Vf.lm = lm(Vf ~ Temp, data = i8out_no3)
summary(i8out_temp_NO3_Vf.lm)
rm(i8out_temp_NO3_Vf.lm)

i8out_PAR_NO3_Vf.lm = lm(Vf ~ PAR, data = i8out_no3)
summary(i8out_PAR_NO3_Vf.lm)
rm(i8out_PAR_NO3_Vf.lm)

i8out_Q_NO3_Vf.lm = lm(Vf ~ Q, data = i8out_no3)
summary(i8out_Q_NO3_Vf.lm)
rm(i8out_Q_NO3_Vf.lm)

i8out_N_NO3_Vf.lm = lm(Vf ~ Conc, data = i8out_no3)
summary(i8out_N_NO3_Vf.lm)
rm(i8out_N_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at I8-Out
i8out_temp_PVf.lm = lm(Vf ~ Temp, data = i8out_po4)
summary(i8out_temp_PVf.lm)
rm(i8out_temp_PVf.lm)

i8out_PAR_PVf.lm = lm(Vf ~ PAR, data = i8out_po4)
summary(i8out_PAR_PVf.lm)
rm(i8out_PAR_PVf.lm)

i8out_Q_PVf.lm = lm(Vf ~ Q, data = i8out_po4)
summary(i8out_Q_PVf.lm)
rm(i8out_Q_PVf.lm)

i8out_P_PVf.lm = lm(Vf ~ Conc, data = i8out_po4)
summary(i8out_P_PVf.lm)
rm(i8out_P_PVf.lm)

```


Do regressions for P-In alone
```{r}
pin <- data %>%
  filter(Site == 'P-In')

pin_nh4 <- pin %>% 
  filter(nutrient == 'NH4-N')

pin_no3 <- pin %>% 
  filter(nutrient == 'NO3-N')

pin_po4 <- pin %>% 
  filter(nutrient == 'PO4-P')

```


Here are the regressions of physical parameters vs Vf for P-In
```{r}

#Get summary stats for lm on NH4_Vf at P-In
pin_temp_NH4_Vf.lm = lm(Vf ~ Temp, data = pin_nh4)
summary(pin_temp_NH4_Vf.lm)
rm(pin_temp_NH4_Vf.lm)

pin_PAR_NH4_Vf.lm = lm(Vf ~ PAR, data = pin_nh4)
summary(pin_PAR_NH4_Vf.lm)
rm(pin_PAR_NH4_Vf.lm)

pin_Q_NH4_Vf.lm = lm(Vf ~ Q, data = pin_nh4)
summary(pin_Q_NH4_Vf.lm)
rm(pin_Q_NH4_Vf.lm)

pin_N_NH4_Vf.lm = lm(Vf ~ Conc, data = pin_nh4)
summary(pin_N_NH4_Vf.lm)
rm(pin_N_NH4_Vf.lm)

#Get summary stats for lm on NO3_Vf at P-In
pin_temp_NO3_Vf.lm = lm(Vf ~ Temp, data = pin_no3)
summary(pin_temp_NO3_Vf.lm)
rm(pin_temp_NO3_Vf.lm)

pin_PAR_NO3_Vf.lm = lm(Vf ~ PAR, data = pin_no3)
summary(pin_PAR_NO3_Vf.lm)
rm(pin_PAR_NO3_Vf.lm)

pin_Q_NO3_Vf.lm = lm(Vf ~ Q, data = pin_no3)
summary(pin_Q_NO3_Vf.lm)
rm(pin_Q_NO3_Vf.lm)

pin_N_NO3_Vf.lm = lm(Vf ~ Conc, data = pin_no3)
summary(pin_N_NO3_Vf.lm)
rm(pin_N_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at P-In
pin_temp_PVf.lm = lm(Vf ~ Temp, data = pin_po4)
summary(pin_temp_PVf.lm)
rm(pin_temp_PVf.lm)

pin_PAR_PVf.lm = lm(Vf ~ PAR, data = pin_po4)
summary(pin_PAR_PVf.lm)
rm(pin_PAR_PVf.lm)

pin_Q_PVf.lm = lm(Vf ~ Q, data = pin_po4)
summary(pin_Q_PVf.lm)
rm(pin_Q_PVf.lm)

pin_P_PVf.lm = lm(Vf ~ Conc, data = pin_po4)
summary(pin_P_PVf.lm)
rm(pin_P_PVf.lm)


```


Aggregate regression analyses on physical params for NH4
```{r}

nh4 <- data %>% 
  filter(nutrient == 'NH4-N')

nh4_temp_Vf.lm = lm(Vf ~ Temp, data = nh4)
summary(nh4_temp_Vf.lm)
rm(nh4_temp_Vf.lm)

nh4_PAR_Vf.lm = lm(Vf ~ PAR, data = nh4)
summary(nh4_PAR_Vf.lm)
rm(nh4_PAR_Vf.lm)

nh4_Q_Vf.lm = lm(Vf ~ Q, data = nh4)
summary(nh4_Q_Vf.lm)
rm(nh4_Q_Vf.lm)

nh4_conc_Vf.lm = lm(Vf ~ Conc, data = nh4)
summary(nh4_conc_Vf.lm)
rm(nh4_conc_Vf.lm)

```


Aggregate regression analyses on physical params for NO3
```{r}

no3 <- data %>% 
  filter(nutrient == 'NO3-N')

no3_temp_Vf.lm = lm(Vf ~ Temp, data = no3)
summary(no3_temp_Vf.lm)
rm(no3_temp_Vf.lm)

no3_PAR_Vf.lm = lm(Vf ~ PAR, data = no3)
summary(no3_PAR_Vf.lm)
rm(no3_PAR_Vf.lm)

no3_Q_Vf.lm = lm(Vf ~ Q, data = no3)
summary(no3_Q_Vf.lm)
rm(no3_Q_Vf.lm)

no3_conc_Vf.lm = lm(Vf ~ Conc, data = no3)
summary(no3_conc_Vf.lm)
rm(no3_conc_Vf.lm)

```


Aggregate regression analyses on physical params for PO4
```{r}

po4 <- data %>% 
  filter(nutrient == 'PO4-P')

po4_temp_Vf.lm = lm(Vf ~ Temp, data = po4)
summary(po4_temp_Vf.lm)
rm(po4_temp_Vf.lm)

po4_PAR_Vf.lm = lm(Vf ~ PAR, data = po4)
summary(po4_PAR_Vf.lm)
rm(po4_PAR_Vf.lm)

po4_Q_Vf.lm = lm(Vf ~ Q, data = po4)
summary(po4_Q_Vf.lm)
rm(po4_Q_Vf.lm)

po4_conc_Vf.lm = lm(Vf ~ Conc, data = po4)
summary(po4_conc_Vf.lm)
rm(po4_conc_Vf.lm)

```


Here are the regressions for Vf and metabolism at I8-In
```{r}

#Get summary stats for lm on NH4_Vf at I8-In
i8in_ER_NH4_Vf.lm = lm(Vf ~ ER, data = i8in_nh4)
summary(i8in_ER_NH4_Vf.lm)
rm(i8in_ER_NH4_Vf.lm)

i8in_GPP_NH4_Vf.lm = lm(Vf ~ GPP, data = i8in_nh4)
summary(i8in_GPP_NH4_Vf.lm)
rm(i8in_GPP_NH4_Vf.lm)

#Get summary stats for lm on NO3_Vf at I8-In
i8in_ER_NO3_Vf.lm = lm(Vf ~ ER, data = i8in_no3)
summary(i8in_ER_NO3_Vf.lm)
rm(i8in_ER_NO3_Vf.lm)

i8in_GPP_NO3_Vf.lm = lm(Vf ~ GPP, data = i8in_no3)
summary(i8in_GPP_NO3_Vf.lm)
rm(i8in_GPP_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at I8-In
i8in_ER_PVf.lm = lm(Vf ~ ER, data = i8in_po4)
summary(i8in_ER_PVf.lm)
rm(i8in_ER_PVf.lm)

i8in_GPP_PVf.lm = lm(Vf ~ GPP, data = i8in_po4)
summary(i8in_GPP_PVf.lm)
rm(i8in_GPP_PVf.lm)
```


Here are the regressions for Vf and metabolism at I8-Out
```{r}

#Get summary stats for lm on NH4_Vf at I8-Out
i8out_ER_NH4_Vf.lm = lm(Vf ~ ER, data = i8out_nh4)
summary(i8out_ER_NH4_Vf.lm)
rm(i8out_ER_NH4_Vf.lm)

i8out_GPP_NH4_Vf.lm = lm(Vf ~ GPP, data = i8out_nh4)
summary(i8out_GPP_NH4_Vf.lm)
rm(i8out_GPP_NH4_Vf.lm)

#Get summary stats for lm on NO3_Vf at I8-Out
i8out_ER_NO3_Vf.lm = lm(Vf ~ ER, data = i8out_no3)
summary(i8out_ER_NO3_Vf.lm)
rm(i8out_ER_NO3_Vf.lm)

i8out_GPP_NO3_Vf.lm = lm(Vf ~ GPP, data = i8out_no3)
summary(i8out_GPP_NO3_Vf.lm)
rm(i8out_GPP_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at I8-Out
i8out_ER_PVf.lm = lm(Vf ~ ER, data = i8out_po4)
summary(i8out_ER_PVf.lm)
rm(i8out_ER_PVf.lm)

i8out_GPP_PVf.lm = lm(Vf ~ GPP, data = i8out_po4)
summary(i8out_GPP_PVf.lm)
rm(i8out_GPP_PVf.lm)

```


Here are the regressions for Vf and metabolism at P-In
```{r}

#Get summary stats for lm on NH4_Vf at P-In
pin_ER_NH4_Vf.lm = lm(Vf ~ ER, data = pin_nh4)
summary(pin_ER_NH4_Vf.lm)
rm(pin_ER_NH4_Vf.lm)

pin_GPP_NH4_Vf.lm = lm(Vf ~ GPP, data = pin_nh4)
summary(pin_GPP_NH4_Vf.lm)
rm(pin_GPP_NH4_Vf.lm)

#Get summary stats for lm on NH4_Vf at P-In
pin_ER_NO3_Vf.lm = lm(Vf ~ ER, data = pin_no3)
summary(pin_ER_NO3_Vf.lm)
rm(pin_ER_NO3_Vf.lm)

pin_GPP_NO3_Vf.lm = lm(Vf ~ GPP, data = pin_no3)
summary(pin_GPP_NO3_Vf.lm)
rm(pin_GPP_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at P-In
pin_ER_PVf.lm = lm(Vf ~ ER, data = pin_po4)
summary(pin_ER_PVf.lm)
rm(pin_ER_PVf.lm)

pin_GPP_PVf.lm = lm(Vf ~ GPP, data = pin_po4)
summary(pin_GPP_PVf.lm)
rm(pin_GPP_PVf.lm)

```


Here are the aggregated regressions for Vf and metabolism
```{r}

#Get summary stats for lm on NH4_Vf
ER_NH4_Vf.lm = lm(Vf ~ ER, data = nh4)
summary(ER_NH4_Vf.lm)
rm(ER_NH4_Vf.lm)

GPP_NH4_Vf.lm = lm(Vf ~ GPP, data = nh4)
summary(GPP_NH4_Vf.lm)
rm(GPP_NH4_Vf.lm)

#Get summary stats for lm on NH4_Vf at P-In
ER_NO3_Vf.lm = lm(Vf ~ ER, data = no3)
summary(ER_NO3_Vf.lm)
rm(ER_NO3_Vf.lm)

GPP_NO3_Vf.lm = lm(Vf ~ GPP, data = no3)
summary(GPP_NO3_Vf.lm)
rm(GPP_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at P-In
ER_PVf.lm = lm(Vf ~ ER, data = po4)
summary(ER_PVf.lm)
rm(ER_PVf.lm)

GPP_PVf.lm = lm(Vf ~ GPP, data = po4)
summary(GPP_PVf.lm)
rm(GPP_PVf.lm)

```

