---
title: "csasn_tascc_no3"
author: "tim covino"
date: "9/19/2020"
output: html_document
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(viridis) 
library(kableExtra)
library(knitr)
library(lubridate)
library(here)
library(ggplot2)
library(plotly)
library(ggthemes)
library(broom)
library(dplyr)
install.packages("psych")          
library("psych")                   
```

##Load data
```{r}
df <- read_csv(here('data', 'I8_out_9_2_11_a.csv'))
Date = '9/2/11'
Site = 'I8-Out'
```

##Truncate data set to clip tails if needed
```{r}
ggplotly(ggplot(df,aes(x=Time, y=Cl)) +
  geom_point() + 
  theme_few())


df <- df %>%  
  mutate(Time = as_hms(Time)) %>% 
      filter(Time >= hms::as_hms('13:20:00'),
             Time <= hms::as_hms('14:04:00'))

```


## Some TASCC stuff: here is Inj-A, which is Cl, and NO3
```{r}
#Let's declare some variables
NaCl_inj <- 4017.07
NaNO3 <- 45.6
cl_inj <- NaCl_inj*(0.6066) 
no3_n_inj <- NaNO3*(0.1648)


Q <- 43.8
w <- 2.5
dist <- 260
no3_cl_inj <- (no3_n_inj/cl_inj)
log_no3_cl_inj <- log(no3_cl_inj)

```

##Background corrections
```{r}
#Now background correct the BTC data
bg_no3 <- min(df$NO3_N, na.rm = TRUE)
df <- mutate(df, cor_no3 = NO3_N - bg_no3*0.9975)


df <- mutate(df, cl_ug = Cl*1000)
bg_cl <- min(df$cl_ug, na.rm = TRUE)
df <- mutate(df, cor_cl = cl_ug - bg_cl*0.9975) 

```

##Calculate total concentration
```{r}
df <- mutate(df, con_no3 = no3_cl_inj * cor_cl)
df <- mutate(df, con_amb_no3 = con_no3 + bg_no3)

df <- df %>%
  rowwise() %>% 
  mutate(tot_no3 = geometric.mean(c(con_amb_no3, NO3_N), na.rm=T)) 
```

##Make TASCC calcs
```{r}
#create a vector of nutrient to conservative tracer ratios and calculate Sw-add values
df <- mutate(df, dt = Time - 13:02)
             
             
df <- mutate(df, no3_cl = cor_no3/cor_cl)
df <- mutate(df, no3_cl = replace (no3_cl, which(no3_cl>no3_cl_inj), NA))
df <- mutate(df, log_no3_cl = log(no3_cl))
df <- mutate(df, diff = log_no3_cl - log_no3_cl_inj)
df <- mutate(df, kw_no3 = diff/dist) 
df <- mutate(df, sw_no3 = -1/kw_no3)
```


##Plot Sw vs. concentration and inspect relationship
```{r}

ggplotly(ggplot(df, aes(x = Time, y = sw_no3)) +
  geom_point(size = 3) +
  geom_line() +
  theme_few())

ggplotly(ggplot(df, aes(x =tot_no3, y = sw_no3, color = btc)) +
  geom_point() +
  #geom_line() +
  theme_few() +
  stat_smooth(aes(group = 1), method='lm', color = 'black'))

```


##Remove outliers through visual inspection. It is often necessary to remove values on the tails. 
```{r}

df <- mutate(df, sw_no3 = replace (sw_no3, which(sw_no3<0), NA))  ##Enforce non-negativity. This is a double check as we've already done this with removing nut/cl values above the injectate value.
df <- mutate(df, sw_no3 = replace (sw_no3, which(sw_no3>20000), NA))  ##Remove high outliers

```


##Fit linear model and retrieve paramater values
```{r}
sw_no3.lm = lm(sw_no3 ~ tot_no3, data=df)
summary(sw_no3.lm)
```

##Do conversions to get other ambient spiralling metrics
```{r}
#get Sw-amb value from summary of sw.lm
Sw_amb_no3 = 678.46  # units are m

#Convert Sw-amb to U-amb
U_amb_no3 = ((Q * bg_no3)/(Sw_amb_no3 *w)) * 60  # units are ug/m2/min

#Convert U-amb to Vf-amb
Vf_amb_no3 = U_amb_no3/bg_no3  # units are mm/mi

sum <- c(Vf_amb_no3, Date, Site) 
print(sum)   


```




