---
title: "csasn_10_28_19"
author: "Tim Covino"
date: "October 28, 2019"
output: word_document
---

```{r setup, echo=F, message=F }
library(tidyverse)
library(kableExtra)
library(knitr)
library(rnoaa)
library(lubridate)
library(here)
library(ggplot2)
library(plotly)
library(ggthemes)
library(broom)
library(dplyr)
library(scales)
library(readxl)
library(cowplot)
library(xlsx)
```

## R Markdown
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
data <- read_csv(here('/data', 'csasn_vf_metab_env_p_values_long_11_13_20.csv'))

na <- read_csv(here('/data', 'csasn_vf_metab_env_p_values_NA.csv')) #this includes the 0 uptake measurements

par <- read_xlsx(here('data/PAR_2011.xlsx'))

c <- read_xlsx(here('data/Q_C_rain_data.xlsx'))

```

data wrangling
```{r}

data <- data %>%
  mutate(Date = mdy(Date)) %>%
  mutate(ID = paste(Site, nutrient, sep=" ")) %>%
  mutate(year = year(Date))

str(d2)

  
d2 <- data %>%
  filter(year == 2011)

par <- par %>%
  rename(par = `PAR (quantum)`)

par <- par %>%
  filter(Date >= ('2011-06-04') & Date <= ('2011-09-09'))

lims <- as.POSIXct(strptime(c("2011-06-01","2011-09-15"), format = "%Y-%m-%d")) 


```

Ggplotly for exploration
```{r}


po4 <- data %>% 
  filter(nutrient == 'PO4-P')

nh4 <- data %>% 
  filter(nutrient == 'NH4-N')

no3 <- data %>% 
  filter(nutrient == 'NO3-N')

f <- ggplot(no3, aes(x = Date, y = Vf, color = 'Site')) + 
  geom_point() + 
  geom_line() +
  theme_few()


g <- ggplotly(f)

g       
max(df$PO4)
```


Plot time series of Vf
```{r}
png(filename = 'ms/response_to_review/figs/Vf_time_series.png',width=9,height=5,
    units='in',res=300)

ggplot(data, aes(x = Date, y = Vf, shape = ID, color = ID)) +
  geom_point(size = 4) +
  theme_few(base_size = 18) +
  theme(legend.title=element_blank()) +
  ylab(expression(V[f-amb]~(mm~min^-1))) +
  xlab('') +
  scale_x_datetime(limits = lims) +
  theme(legend.position = 'bottom') +
  theme(panel.grid.major.x = element_line( size = 0.3, color= 'black', linetype = 'dashed')) +
  #theme(legend.position = c(0.3, 0.75)) +
  #theme(text = element_text(size=16)) +
  scale_shape_manual(values = c(16, 16, 16, 15, 15, 15, 17, 17, 17)) +
  scale_color_manual(values = c('dodgerblue', 'darkgreen', 'deeppink', 'dodgerblue', 'darkgreen',  'deeppink', 'dodgerblue', 'darkgreen', 'deeppink'))

dev.off()

```

Plot time series of PAR
```{r}
png(filename = 'ms/response_to_review/figs/par_time_series.png',width=8,height=2.5, units='in', res=300)

ggplot(par, aes(x = Date, y = par)) +
  geom_point(size = 2, color = 'red') +
  geom_line(color = 'red', linetype = 'dashed') +
  theme_few(base_size = 14) +
  theme(panel.grid.major.x = element_line( size = 0.3, color= 'black', linetype = 'dashed')) +
  theme(legend.title=element_blank()) +
  ylab(expression(PAR~(mu*mol~m^-2~d^-1))) +
  xlab('') +
  scale_x_datetime(date_labels = "%m/%d/%y", limits = lims) +
  theme(legend.position = 'none') #+
  theme(text = element_text(size=16)) 

dev.off()

```

Plot time series of nutrient concs.

```{r}
ggplot(d2, aes(x = Date, y = Conc, color = nutrient)) +
  geom_point(size = 2) +
  geom_line(linetype = 'dashed') +
  theme_few(base_size = 14) 

head(d2)

```

Plot NH4-Vf vs Temperature
```{r}
png(filename = 'ms/response_to_review/figs/temp_NH4_Vf.png',width=4,height=4,
    units='in',res=300)

t1 <- ggplot(na, aes(x = Temp, y = NH4_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(NH[4]-N~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(Temperature~(degree*C))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))

dev.off()


temp_NH4_Vf.lm = lm(NH4_Vf ~ Temp, data=na)
summary(temp_NH4_Vf.lm)

```


Plot NO3-Vf vs Temperature
```{r}
png(filename = 'ms/response_to_review/figs/temp_NO3_Vf.png',width=4,height=4,
    units='in',res=300)

t2 <- ggplot(na, aes(x = Temp, y = NO3_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(NO[3]-N~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(Temperature~(degree*C))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))

dev.off()

temp_NO3_Vf.lm = lm(NO3_Vf ~ Temp, data=na)
summary(temp_NO3_Vf.lm)

```


Plot P-Vf vs Temperature
```{r}
png(filename = 'ms/response_to_review/figs/temp_P_Vf.png',width=4,height=4,
    units='in',res=300)

t3 <- ggplot(na, aes(x = Temp, y = P_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(PO[4]-P~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(Temperature~(degree*C))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink')) 

dev.off()

temp_P_Vf.lm = lm(P_Vf ~ Temp, data=na)
summary(temp_P_Vf.lm)

```


Plot NH4-Vf vs PAR
```{r}
png(filename = 'ms/response_to_review/figs/PAR_NH4_Vf.png',width=4,height=4,
    units='in',res=300)

p1 <- ggplot(na, aes(x = PAR, y = NH4_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(NH[4]-N~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(PAR~(mu*mol~m^-2~d^-1))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))

dev.off()

PAR_NH4_Vf.lm = lm(NH4_Vf ~ PAR, data=na)
summary(PAR_NH4_Vf.lm)
```


Plot NO3-Vf vs PAR
```{r}
png(filename = 'ms/response_to_review/figs/PAR_NO3_Vf.png',width=4,height=4,
    units='in',res=300)

p2 <- ggplot(na, aes(x = PAR, y = NO3_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(NO[3]-N~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(PAR~(mu*mol~m^-2~d^-1))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))

dev.off()

PAR_NO3_Vf.lm = lm(NO3_Vf ~ PAR, data=na)
summary(PAR_NO3_Vf.lm)
```


Plot P-Vf vs PAR
```{r}
png(filename = 'ms/response_to_review/figs/PAR_P_Vf.png',width=4,height=4,
    units='in',res=300)

p3 <- ggplot(na, aes(x = PAR, y = P_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(PO[4]-P~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(PAR~(mu*mol~m^-2~d^-1))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink')) 

dev.off()

PAR_P_Vf.lm = lm(P_Vf ~ PAR, data=na)
summary(PAR_P_Vf.lm)
```


Plot NH4-Vf vs Q
```{r}
png(filename = 'ms/response_to_review/figs/Q_NH4_Vf.png',width=4,height=4,
    units='in',res=300)

q1 <- ggplot(na, aes(x = Q, y = NH4_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(NH[4]-N~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(Q~(L~s^-1))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))

dev.off()

Q_NH4_Vf.lm = lm(NH4_Vf ~ Q, data=na)
summary(Q_NH4_Vf.lm)
```


Plot NO3-Vf vs Q
```{r}
png(filename = 'ms/response_to_review/figs/Q_NO3_Vf.png',width=4,height=4,
    units='in',res=300)

q2 <- ggplot(na, aes(x = Q, y = NO3_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(NO[3]-N~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(Q~(L~s^-1))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))

dev.off()

Q_NO3_Vf.lm = lm(NO3_Vf ~ Q, data=na)
summary(Q_NO3_Vf.lm)
```


Plot P-Vf vs Q
```{r}
png(filename = 'ms/response_to_review/figs/Q_P_Vf.png',width=4,height=4,
    units='in',res=300)

q3 <- ggplot(na, aes(x = Q, y = P_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(PO[4]-P~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(Q~(L~s^-1))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))  
  #stat_smooth(aes(group = 1), method='lm', color = 'black')

dev.off()

Q_P_Vf.lm = lm(P_Vf ~ Q, data=na)
summary(Q_P_Vf.lm)
```

Create grid of physical regressions (Figure 5)
```{r}
png(filename = 'ms/response_to_review/figs/phys_regs.png',width=9, height=9,
    units='in',res=300)

plot_grid(t1, t2, t3, p1, p2, p3, q1, q2, q3, ncol = 3, nrow = 3, align = 'hv')

dev.off()

```



Plot Vf vs NH4 concentration
```{r}
png(filename = 'ms/response_to_review/figs/conc_NH4_Vf.png',width=4,height=4,
    units='in',res=300)

c1 <- ggplot(na, aes(x = NH4, y = NH4_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(NH[4]-N~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(Ambient~NH[4]-N~(mu*g~L^-1))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink')) 
  #stat_smooth(aes(group = 1), method='lm', color = 'black')

dev.off()

NH4_conc_Vf.lm = lm(NH4_Vf ~ NH4, data=na)
summary(NH4_conc_Vf.lm)

```


Plot Vf vs NO3 concentration
```{r}
png(filename = 'ms/response_to_review/figs/conc_NO3_Vf.png',width=4,height=4,
    units='in',res=300)

c2 <- ggplot(na, aes(x = NO3, y = NO3_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(NO[3]-N~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(Ambient~NO[3]-N~(mu*g~L^-1))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink')) 
  #stat_smooth(aes(group = 1), method='lm', color = 'black')

dev.off()

NO3_conc_Vf.lm = lm(NO3_Vf ~ NO3, data=na)
summary(NO3_conc_Vf.lm)

```


Plot Vf vs PO4 concentration
```{r}
png(filename = 'ms/response_to_review/figs/conc_NO3_Vf.png',width=4,height=4,
    units='in',res=300)

c3 <- ggplot(na, aes(x = PO4, y = P_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(PO[4]-P~V[f-amb]~(mm/min))) +
  ylim(0, 41) +
  xlab(expression(Ambient~PO[4]-P~(mu*g/L))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink')) 

c3
dev.off()

P_conc_Vf.lm = lm(P_Vf ~ PO4, data=na)
summary(P_conc_Vf.lm)

```


Create grid of concentration regressions (Figure 6)
```{r}
png(filename = 'ms/response_to_review/figs/conc_regs.png',width=10, height=3,
    units='in',res=300)

plot_grid(c1, c2, c3, ncol = 3, nrow = 1, align = 'hv')

dev.off()

```


#Plot NH4_Vf vs ER
```{r}
png(filename = 'ms/response_to_review/figs/ER_NH4_Vf.png', width=4, height=4,
    units='in',res=300)

m1 <- ggplot(na, aes(x = ER, y = NH4_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(NH[4]-N~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(ER~(mg~O[2]~m^-2~d^-1))) +
  theme(legend.position = 'none') +
  scale_x_reverse() +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))
  

dev.off()

#Get summary stats for lm
ER_NH4_Vf.lm = lm(NH4_Vf ~ ER, data = na)
summary(ER_NH4_Vf.lm)
```


#Plot NO3_Vf vs ER
```{r}
png(filename = 'ms/response_to_review/figs/ER_NO3_Vf.png', width=4, height=4,
    units='in',res=300)

m2 <- ggplot(na, aes(x = ER, y = NO3_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(NO[3]-N~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(ER~(mg~O[2]~m^-2~d^-1))) +
  theme(legend.position = 'none') +
  scale_x_reverse() +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))
  

dev.off()

#Get summary stats for lm
ER_NO3_Vf.lm = lm(NO3_Vf ~ ER, data = na)
summary(ER_NO3_Vf.lm)
```


#Plot P_Vf vs ER
```{r}
png(filename = 'ms/response_to_review/figs/ER_PO4_Vf.png',width=4,height=4,
    units='in',res=300)

m3 <- ggplot(na, aes(x = ER, y = P_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(PO[4]-P~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(ER~(mg~O[2]~m^-2~d^-1))) +
  theme(legend.position = 'none') +
  scale_x_reverse() +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))

dev.off()

ER_P_Vf.lm = lm(P_Vf ~ ER, data=na)
summary(ER_P_Vf.lm)

```


#Plot NH4_Vf vs GPP
```{r}
png(filename = 'ms/response_to_review/figs/GPP_NH4_Vf.png',width=4, height=4,
    units='in',res=300)

m4 <- ggplot(na, aes(x = GPP, y = NH4_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(NH[4]-N~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(GPP~(mg~O[2]~m^-2~d^-1))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))

dev.off()

#Get summary stats for lm
GPP_NH4_Vf.lm = lm(NH4_Vf ~ GPP, data = na)
summary(GPP_NH4_Vf.lm)
```


#Plot NO3_Vf vs GPP
```{r}
png(filename = 'ms/response_to_review/figs/GPP_NO3_Vf.png',width=4, height=4,
    units='in',res=300)

m5 <- ggplot(na, aes(x = GPP, y = NO3_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(NO[3]-N~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(GPP~(mg~O[2]~m^-2~d^-1))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))

dev.off()

#Get summary stats for lm
GPP_NO3_Vf.lm = lm(NO3_Vf ~ GPP, data = na)
summary(GPP_NO3_Vf.lm)
```


#Plot P_Vf vs GPP
```{r}
png(filename = 'ms/response_to_review/figs/GPP_PO4_Vf.png',width=4,height=4,
    units='in',res=300)

m6 <- ggplot(na, aes(x = GPP, y = P_Vf, shape = Site, color = Site)) +
  geom_point(size = 3) +
  theme_few(base_size = 14) +
  theme(legend.title=element_blank()) +
  ylab(expression(PO[4]-P~V[f-amb]~(mm~min^-1))) +
  ylim(0, 41) +
  xlab(expression(GPP~(mg~O[2]~m^-2~d^-1))) +
  theme(legend.position = 'none') +
  scale_shape_manual(values = c(16,15,17)) +
  scale_color_manual(values = c('darkgreen', 'dodgerblue', 'deeppink'))

dev.off()

GPP_PVf.lm = lm(P_Vf ~ GPP, data = na)
summary(GPP_PVf.lm)
```


Create grid of metabolic regressions (Figure 7)
```{r}
png(filename = 'ms/response_to_review/figs/met_regs.png',width=10, height=6,
    units='in',res=300)

plot_grid(m1, m2, m3, m4, m5, m6, ncol = 3, nrow = 2, align = 'hv')

dev.off()

```



The chunks above are used for the figures in the paper. The chunks below are to evaluate the linear models at each individual site, as opposed to linear regressions on aggregated data. 

Do regressions for I8-In alone
```{r}
i8in <- data %>%
  filter(Site == 'I8-In')

i8in_wide <- i8in %>% 
  pivot_wider(names_from = nutrient, values_from = Conc)

i8in_nh4 <- i8in %>% 
  filter(nutrient == 'NH4-N')

i8in_po4 <- i8in %>% 
  filter(nutrient == 'PO4-P')
```


Here are the regressions of physical parameters vs Vf for I8-In
```{r}

#Get summary stats for lm on NH4_Vf at I8-In
i8in_temp_NH4_Vf.lm = lm(Vf ~ Temp, data = i8in_nh4)
summary(i8in_temp_NH4_Vf.lm)
rm(i8in_temp_NH4_Vf.lm)

i8in_PAR_NH4_Vf.lm = lm(Vf ~ PAR, data = i8in_nh4)
summary(i8in_PAR_NH4_Vf.lm)
rm(i8in_PAR_NH4_Vf.lm)

i8in_Q_NH4_Vf.lm = lm(Vf ~ Q, data = i8in_nh4)
summary(i8in_Q_NH4_Vf.lm)
rm(i8in_Q_NH4_Vf.lm)

i8in_N_NH4_Vf.lm = lm(Vf ~ Conc, data = i8in_nh4)
summary(i8in_N_NH4_Vf.lm)
rm(i8in_N_NH4_Vf.lm)

#Get summary stats for lm on NO3_Vf at I8-In
i8in_temp_NO3_Vf.lm = lm(NO3_Vf ~ Temp, data = i8in_no3)
summary(i8in_temp_NO3_Vf.lm)
rm(i8in_temp_NO3_Vf.lm)

i8in_PAR_NO3_Vf.lm = lm(NO3_Vf ~ PAR, data = i8in_no3)
summary(i8in_PAR_NO3_Vf.lm)
rm(i8in_PAR_NO3_Vf.lm)

i8in_Q_NO3_Vf.lm = lm(NO3_Vf ~ Q, data = i8in_no3)
summary(i8in_Q_NO3_Vf.lm)
rm(i8in_Q_NO3_Vf.lm)

i8in_N_NO3_Vf.lm = lm(NO3_Vf ~ NO3, data = i8in_no3)
summary(i8in_N_NO3_Vf.lm)
rm(i8in_N_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at I8-In
i8in_temp_PVf.lm = lm(Vf ~ Temp, data = i8in_po4)
summary(i8in_temp_PVf.lm)
rm(i8in_temp_PVf.lm)


i8in_PAR_PVf.lm = lm(Vf ~ PAR, data = i8in_po4)
summary(i8in_PAR_PVf.lm)
rm(i8in_PAR_PVf.lm)

i8in_Q_PVf.lm = lm(Vf ~ Q, data = i8in_po4)
summary(i8in_Q_PVf.lm)
rm(i8in_Q_PVf.lm)

i8in_P_PVf.lm = lm(Vf ~ Conc, data = i8in_po4)
summary(i8in_P_PVf.lm)
rm(i8in_P_PVf.lm)


```


Generic plotting for visual assessment of data
```{r}

ggplot(i8in,aes(x=PO4, y=P_Vf, color = Site)) + geom_point() + 
  #ylab(expression(NH[4]-N~V[f-amb]~(mm/min))) + 
  theme_bw(base_size = 16) +
  #xlab(expression ("GPP (g/m"^2*"/d)")) +
  geom_smooth(method='lm', color = "black")

```


Do regressions for I8-Out alone
```{r}
i8out <- data %>%
  filter(Site == 'I8-Out')

i8out_nh4 <- i8out %>% 
  filter(nutrient == 'NH4-N')

i8out_no3 <- i8out %>% 
  filter(nutrient == 'NO3-N')

i8out_po4 <- i8out %>% 
  filter(nutrient == 'PO4-P')

```


Here are the regressions of physical parameters vs Vf for I8-Out
```{r}

#Get summary stats for lm on NH4_Vf at I8-Out
i8out_temp_NH4_Vf.lm = lm(Vf ~ Temp, data = i8out_nh4)
summary(i8out_temp_NH4_Vf.lm)
rm(i8out_temp_NH4_Vf.lm)

i8out_PAR_NH4_Vf.lm = lm(Vf ~ PAR, data = i8out_nh4)
summary(i8out_PAR_NH4_Vf.lm)
rm(i8out_PAR_NH4_Vf.lm)

i8out_Q_NH4_Vf.lm = lm(Vf ~ Q, data = i8out_nh4)
summary(i8out_Q_NH4_Vf.lm)
rm(i8out_Q_NH4_Vf.lm)

i8out_N_NH4_Vf.lm = lm(Vf ~ Conc, data = i8out_nh4)
summary(i8out_N_NH4_Vf.lm)
rm(i8out_N_NH4_Vf.lm)

#Get summary stats for lm on NO3_Vf at I8-Out
i8out_temp_NO3_Vf.lm = lm(Vf ~ Temp, data = i8out_no3)
summary(i8out_temp_NO3_Vf.lm)
rm(i8out_temp_NO3_Vf.lm)

i8out_PAR_NO3_Vf.lm = lm(Vf ~ PAR, data = i8out_no3)
summary(i8out_PAR_NO3_Vf.lm)
rm(i8out_PAR_NO3_Vf.lm)

i8out_Q_NO3_Vf.lm = lm(Vf ~ Q, data = i8out_no3)
summary(i8out_Q_NO3_Vf.lm)
rm(i8out_Q_NO3_Vf.lm)

i8out_N_NO3_Vf.lm = lm(Vf ~ Conc, data = i8out_no3)
summary(i8out_N_NO3_Vf.lm)
rm(i8out_N_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at I8-Out
i8out_temp_PVf.lm = lm(Vf ~ Temp, data = i8out_po4)
summary(i8out_temp_PVf.lm)
rm(i8out_temp_PVf.lm)

i8out_PAR_PVf.lm = lm(Vf ~ PAR, data = i8out_po4)
summary(i8out_PAR_PVf.lm)
rm(i8out_PAR_PVf.lm)

i8out_Q_PVf.lm = lm(Vf ~ Q, data = i8out_po4)
summary(i8out_Q_PVf.lm)
rm(i8out_Q_PVf.lm)

i8out_P_PVf.lm = lm(Vf ~ Conc, data = i8out_po4)
summary(i8out_P_PVf.lm)
rm(i8out_P_PVf.lm)

```


Generic plotting for visualizing data
```{r}
ggplot(i8out_po4, aes(x = Conc, y = Vf)) + geom_point() + 
  #ylab(expression(NH[4]-N~V[f-amb]~(mm/min))) + 
  theme_bw(base_size = 16) +
  #xlab(expression(Temperature~(degree*C))) +
  geom_smooth(method='lm')

```


Do regressions for P-In alone
```{r}
pin <- data %>%
  filter(Site == 'P-In')

pin_nh4 <- pin %>% 
  filter(nutrient == 'NH4-N')

pin_no3 <- pin %>% 
  filter(nutrient == 'NO3-N')

pin_po4 <- pin %>% 
  filter(nutrient == 'PO4-P')

```


Here are the regressions of physical parameters vs Vf for P-In
```{r}

#Get summary stats for lm on NH4_Vf at P-In
pin_temp_NH4_Vf.lm = lm(Vf ~ Temp, data = pin_nh4)
summary(pin_temp_NH4_Vf.lm)
rm(pin_temp_NH4_Vf.lm)

pin_PAR_NH4_Vf.lm = lm(Vf ~ PAR, data = pin_nh4)
summary(pin_PAR_NH4_Vf.lm)
rm(pin_PAR_NH4_Vf.lm)

pin_Q_NH4_Vf.lm = lm(Vf ~ Q, data = pin_nh4)
summary(pin_Q_NH4_Vf.lm)
rm(pin_Q_NH4_Vf.lm)

pin_N_NH4_Vf.lm = lm(Vf ~ Conc, data = pin_nh4)
summary(pin_N_NH4_Vf.lm)
rm(pin_N_NH4_Vf.lm)

#Get summary stats for lm on NO3_Vf at P-In
pin_temp_NO3_Vf.lm = lm(Vf ~ Temp, data = pin_no3)
summary(pin_temp_NO3_Vf.lm)
rm(pin_temp_NO3_Vf.lm)

pin_PAR_NO3_Vf.lm = lm(Vf ~ PAR, data = pin_no3)
summary(pin_PAR_NO3_Vf.lm)
rm(pin_PAR_NO3_Vf.lm)

pin_Q_NO3_Vf.lm = lm(Vf ~ Q, data = pin_no3)
summary(pin_Q_NO3_Vf.lm)
rm(pin_Q_NO3_Vf.lm)

pin_N_NO3_Vf.lm = lm(Vf ~ Conc, data = pin_no3)
summary(pin_N_NO3_Vf.lm)
rm(pin_N_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at P-In
pin_temp_PVf.lm = lm(Vf ~ Temp, data = pin_po4)
summary(pin_temp_PVf.lm)
rm(pin_temp_PVf.lm)

pin_PAR_PVf.lm = lm(Vf ~ PAR, data = pin_po4)
summary(pin_PAR_PVf.lm)
rm(pin_PAR_PVf.lm)

pin_Q_PVf.lm = lm(Vf ~ Q, data = pin_po4)
summary(pin_Q_PVf.lm)
rm(pin_Q_PVf.lm)

pin_P_PVf.lm = lm(Vf ~ Conc, data = pin_po4)
summary(pin_P_PVf.lm)
rm(pin_P_PVf.lm)


```


Generic plotting for visualizing data
```{r}
ggplot(pin, aes(x=PAR, y=P_Vf, color = Site)) + geom_point() + 
  #ylab(expression(NH[4]-N~V[f-amb]~(mm/min))) + 
  theme_bw(base_size = 16) +
  #xlab(expression(Temperature~(degree*C))) +
  geom_smooth(method='lm')

```


Aggregate regression analyses on physical params for NH4
```{r}

nh4 <- data %>% 
  filter(nutrient == 'NH4-N')

nh4_temp_Vf.lm = lm(Vf ~ Temp, data = nh4)
summary(nh4_temp_Vf.lm)
rm(nh4_temp_Vf.lm)

nh4_PAR_Vf.lm = lm(Vf ~ PAR, data = nh4)
summary(nh4_PAR_Vf.lm)
rm(nh4_PAR_Vf.lm)

nh4_Q_Vf.lm = lm(Vf ~ Q, data = nh4)
summary(nh4_Q_Vf.lm)
rm(nh4_Q_Vf.lm)

nh4_conc_Vf.lm = lm(Vf ~ Conc, data = nh4)
summary(nh4_conc_Vf.lm)
rm(nh4_conc_Vf.lm)

```




Here are the regressions for Vf and metabolism at I8-In
```{r}

#Get summary stats for lm on NH4_Vf at I8-In
i8in_ER_NH4_Vf.lm = lm(NH4_Vf ~ ER, data = i8in)
summary(i8in_ER_NH4_Vf.lm)

i8in_GPP_NH4_Vf.lm = lm(NH4_Vf ~ GPP, data = i8in)
summary(i8in_GPP_NH4_Vf.lm)

#Get summary stats for lm on NO3_Vf at I8-In
i8in_ER_NO3_Vf.lm = lm(NO3_Vf ~ ER, data = i8in)
summary(i8in_ER_NO3_Vf.lm)

i8in_GPP_NO3_Vf.lm = lm(NO3_Vf ~ GPP, data = i8in)
summary(i8in_GPP_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at I8-In
i8in_ER_PVf.lm = lm(P_Vf ~ ER, data = i8in)
summary(i8in_ER_PVf.lm)

i8in_GPP_PVf.lm = lm(P_Vf ~ GPP, data = i8in)
summary(i8in_GPP_PVf.lm)

```


Generic plotting for visualizing data
```{r}
ggplot(i8in, aes(x=GPP, y=N_Vf, color = Site)) + geom_point() + 
  ylab(expression(NH[4]-N~V[f-amb]~(mm/min))) + 
  theme_bw(base_size = 16) +
  xlab(expression ("GPP (g/m"^2*"/d)")) +
  geom_smooth(method='lm')
```


Here are the regressions for Vf and metabolism at I8-Out
```{r}

#Get summary stats for lm on NH4_Vf at I8-Out
i8out_ER_NH4_Vf.lm = lm(NH4_Vf ~ ER, data = i8out)
summary(i8out_ER_NH4_Vf.lm)

i8out_GPP_NH4_Vf.lm = lm(NH4_Vf ~ GPP, data = i8out)
summary(i8out_GPP_NH4_Vf.lm)

#Get summary stats for lm on NO3_Vf at I8-Out
i8out_ER_NO3_Vf.lm = lm(NO3_Vf ~ ER, data = i8out)
summary(i8out_ER_NO3_Vf.lm)

i8out_GPP_NO3_Vf.lm = lm(NO3_Vf ~ GPP, data = i8out)
summary(i8out_GPP_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at I8-Out
i8out_ER_PVf.lm = lm(P_Vf ~ ER, data = i8out)
summary(i8out_ER_PVf.lm)

i8out_GPP_PVf.lm = lm(P_Vf ~ GPP, data = i8out)
summary(i8out_GPP_PVf.lm)




```


Here are the regressions for Vf and metabolism at P-In
```{r}

#Get summary stats for lm on NH4_Vf at P-In
pin_ER_NH4_Vf.lm = lm(NH4_Vf ~ ER, data = pin)
summary(pin_ER_NH4_Vf.lm)

pin_GPP_NH4_Vf.lm = lm(NH4_Vf ~ GPP, data = pin)
summary(pin_GPP_NH4_Vf.lm)

#Get summary stats for lm on NH4_Vf at P-In
pin_ER_NO3_Vf.lm = lm(NO3_Vf ~ ER, data = pin)
summary(pin_ER_NO3_Vf.lm)

pin_GPP_NO3_Vf.lm = lm(NO3_Vf ~ GPP, data = pin)
summary(pin_GPP_NO3_Vf.lm)

#Get summary stats for lm on P_Vf at P-In
pin_ER_PVf.lm = lm(P_Vf ~ ER, data = pin)
summary(pin_ER_PVf.lm)

pin_GPP_PVf.lm = lm(P_Vf ~ GPP, data = pin)
summary(pin_GPP_PVf.lm)


#nitrate is 6/28


```



Below this is plotting and older stuff as of 9/14/20

Regression for Vf and metabolism at I8-Out
```{r}
ggplot(i8out, aes(x=GPP, y=N_Vf, color = Site)) + geom_point() + 
  ylab(expression(NH[4]-N~V[f-amb]~(mm/min))) + 
  theme_bw(base_size = 16) +
  xlab(expression ("GPP (g/m"^2*"/d)")) +
  geom_smooth(method='lm')


#Get summary stats for lm
i8out_GPP_NVf.lm = lm(N_Vf ~ GPP, data = i8out)
summary(i8out_GPP_NVf.lm)

ggplot(i8out, aes(x=ER, y=N_Vf, color = Site)) + geom_point() + 
  ylab(expression(NH[4]-N~V[f-amb]~(mm/min))) + 
  theme_bw(base_size = 16) +
  xlab(expression ("ER (g/m"^2*"/d)")) +
  geom_smooth(method='lm')


#Get summary stats for lm
i8out_ER_NVf.lm = lm(N_Vf ~ ER, data = i8out)
summary(i8out_ER_NVf.lm)
```


```{r}
ggplot(i8out, aes(x=GPP, y=P_Vf, color = Site)) + geom_point() + 
  ylab(expression(PO[4]-P~V[f-amb]~(mm/min))) + 
  theme_bw(base_size = 16) +
  xlab(expression ("GPP (g/m"^2*"/d)")) +
  geom_smooth(method='lm')


#Get summary stats for lm
i8out_GPP_PVf.lm = lm(P_Vf ~ GPP, data = i8out)
summary(i8out_GPP_PVf.lm)
```



```{r}
ggplot(i8out, aes(x=ER, y=P_Vf, color = Site)) + geom_point() + 
  ylab(expression(PO[4]-P~V[f-amb]~(mm/min))) + 
  theme_bw(base_size = 16) +
  xlab(expression ("ER (g/m"^2*"/d)")) +
  geom_smooth(method='lm')

#Get summary stats for lm
i8out_ER_PVf.lm = lm(P_Vf ~ ER, data = i8out)
summary(i8out_ER_PVf.lm)
```



```{r}
ggplot(i8in, aes(x=GPP, y=P_Vf, color = Site)) + geom_point() + 
  ylab(expression(PO[4]-P~V[f-amb]~(mm/min))) + 
  theme_bw(base_size = 16) +
  xlab(expression ("GPP (g/m"^2*"/d)")) +
  geom_smooth(method='lm')

#Get summary stats for lm
i8in_ER_PVf.lm = lm(P_Vf ~ ER, data = i8in)
summary(i8in_ER_PVf.lm)
```








