---
title: "csasn_tassc_b"
author: "tim covino"
date: "9/19/2020"
output: html_document
---


```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(kableExtra)
library(knitr)
library(lubridate)
library(here)
library(ggplot2)
library(ggthemes)
library(broom)
library(dplyr)
install.packages("psych")          # Install psych package
library("psych")                   # Load psych package
```

##Load data
```{r}
i8b <- read_csv(here('data', 'I8_out_9_2_11_b.csv'))
```

##Truncate data set to clip tails
```{r}

i8b <- i8b %>%  
  mutate(Time = as_hms(Time)) %>% 
      filter(Time >= hms::as_hms('15:41:00'),
             Time <= hms::as_hms('15:57:00'))

```


## Some TASCC stuff: here is Inj-B, which is Cl, and NH4
```{r}
#Let's declare some variables
NaCl_inj <- 3993.47
NH4Cl <- 79.46
Cl_inj <- NaCl_inj*(0.6066) + NH4Cl*(0.6627)
NH4_N_inj <- NH4Cl*(0.261908)


Q <- 43.8
w <- 2.5
dist <- 260
nh4_cl_inj <- (NH4_N_inj/Cl_inj)
log_nh4_cl_inj <- log(nh4_cl_inj)

```

##Background corrections
```{r}
#Now background correct the BTC data
bg_nh4 <- min(i8b$NH4_N, na.rm = TRUE)
i8b <- mutate(i8b, cor_nh4 = NH4_N - bg_nh4*0.9975)


i8b <- mutate(i8b, cl_ug = Cl*1000)
bg_cl <- min(i8b$cl_ug, na.rm = TRUE)
i8b <- mutate(i8b, cor_cl = cl_ug - bg_cl*0.9975) #i8 <- mutate(i8, cor_cl = Cl - 2450)

```

##Calculate total concentration
```{r}
i8b <- mutate(i8b, con_nh4 = nh4_cl_inj * cor_cl)
i8b <- mutate(i8b, con_amb_nh4 = con_nh4 + bg_nh4)

i8b <- i8b %>%
  rowwise() %>% 
  mutate(tot_nh4 = geometric.mean(c(con_amb_nh4, NH4_N), na.rm=T)) 
```

##Make TASCC calcs
```{r}
#create a vector of nutrient to conservative tracer ratios and calculate Sw-add values
i8b <- mutate(i8b, nh4_cl = cor_nh4/cor_cl)
i8b <- mutate(i8b, log_nh4_cl = log(nh4_cl))
i8b <- mutate(i8b, diff = log_nh4_cl - log_nh4_cl_inj)
i8b <- mutate(i8b, kw = diff/dist) 
i8b <- mutate(i8b, sw = -1/kw)
```


##Plot Sw vs. concentration and inspect relationship
```{r}
ggplot(i8b, aes(x = Time, y = sw)) +
  geom_point(size = 3) +
  theme_few()

ggplot(i8b, aes(x = tot_nh4, y = sw)) +
  geom_point(size = 3) +
  theme_few() +
  stat_smooth(aes(group = 1), method='lm', color = 'black')

```


##Remove outliers through visual inspection. It is often necessary to remove values on the tails. 
```{r}

i8b <- mutate(i8b, sw = replace (sw, which(sw<0), NA))
i8b <- mutate(i8b, sw = replace (sw, which(sw>100), NA))

```


##Fit linear model and retrieve paramater values
```{r}
sw.lm = lm(sw ~ tot_nh4, data=i8b)
summary(sw.lm)
```

##Do conversions to get other ambient spiralling metrics
```{r}
#get Sw-amb value from summary of sw.lm
Sw_amb = 279.36  # units are m

#Convert Sw-amb to U-amb
U_amb = ((Q * bg_nh4)/(Sw_amb *w)) * 60  # units are ug/m2/min

#Convert U-amb to Vf-amb
Vf_amb = U_amb/bg_nh4  # units are mm/min

```




